% GitHub Repo and Documentation: https://github.com/celiobjunior/resume-template
% Copyright © 2025 Celio B Junior. All rights reserved.
% 
% Licensed under the Apache License, Version 2.0 (the "License");
% you may not use this file except in compliance with the License.
% You may obtain a copy of the License at
%
%     http://www.apache.org/licenses/LICENSE-2.0
%
% This template follows best practices from README.md
\documentclass[a4paper,10pt]{article}

% --- PACKAGES ---
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{geometry}
\usepackage{parskip}
\usepackage{hyperref}
\usepackage{xurl}
\usepackage{titlesec}
\usepackage{textcomp}

% --- CONFIGURATIONS ---
\geometry{top=1.0cm, bottom=1.0cm, left=1.0cm, right=1.0cm}
\pagestyle{empty}

% PDF metadata - customize with your information
\hypersetup{
    pdftitle={CV Igor de Paula},
    pdfauthor={Igor de Paula},
    colorlinks=true,
    linkcolor=black,
    urlcolor=black,
    citecolor=black,
    bookmarksdepth=1 
}

\setcounter{secnumdepth}{0}

\titleformat{\section}
  {\Large\bfseries}
  {}
  {0em}
  {}
  [\titlerule\vspace{0.5ex}]

% --- BEGIN DOCUMENT ---
\begin{document}

% --- HEADER SECTION ---
% Replace with your personal information
\begin{center}
    {\LARGE \textbf{Igor Francisco Lima de Paula}} \\ [0.1cm]
    Poços de Caldas, Brazil {\textbullet}
    Email: \href{mailto:igorfldepaula@gmail.com}{igorfldepaula@gmail.com} {\textbullet}
    \href{https://www.linkedin.com/in/igor-fl-de-paula}{linkedin.com/in/igor-fl-de-paula} {\textbullet}
    \href{https://github.com/igorflpaula}{github.com/igorflpaula}
\end{center}

% --- SECTIONS ---    
\section{Experience}
    % List work experience in reverse chronological order (most recent first)
    \subsection*{\texorpdfstring{
        \textbf{Leveduca} \hfill Poços de Caldas, Brazil
        }{
            Leveduca -- Poços de Caldas, Brazil
        }}
    \textit{Mid-Level Software Developer \hfill Feb 2024 - Present}
        \begin{itemize} 
            \item Developed key product features (Gamification, OKRs, Feedback System) that added significant value and boosted sales.
            \item Optimized back-end processes, significantly reducing the execution time of critical tasks.
            \item Contributed to front-end development using Vue.js, implementing dynamic and responsive user interfaces.
            \item Managed integrations with external RESTful APIs and critical business systems, including CRM platforms.
        \end{itemize}
    \textit{Junior Software Developer \hfill Jul 2023 - Jan 2024}
        \begin{itemize} 
            \item Re-architected the company's internal administration system, significantly enhancing usability and efficiency for the team.
            \item Created back-end features using PHP and Laravel and contributed to front-end tasks with HTML, CSS, and Vue.js.
        \end{itemize}
    \textit{IT Assistant \hfill Dec 2022 - Jun 2023}
        \begin{itemize} 
            \item Reduced support ticket volume by proactively analyzing recurring incidents to identify and resolve root causes.
            \item Integrated external APIs with proprietary systems to automate processes and expand platform functionality.
        \end{itemize}
        
\section{Education}
    \subsection*{\texorpdfstring{
        \textbf{Rocketseat} \hfill Remote
        }{
        Rocketseat -- Remote 
        }}
    \textit{Master of Business Administration in Full Stack \hfill Oct 2024 - Oct 2025}
    % Use this format for each degree - most recent first
    \subsection*{\texorpdfstring{
        \textbf{IFSULDEMINAS} \hfill Poços de Caldas, Brazil
        }{
        IFSULDEMINAS -- Poços de Caldas, Brazil
        }}
    \textit{Bachelor's Degree in Computer Engineering \hfill Jan 2017 - Dec 2023}

\section{Leadership Activities} 
    % Include volunteer work, clubs, organizations, or leadership roles
    \subsection*{\texorpdfstring{
        \textbf{Thomas Adam Academic Center} \hfill Poços de Caldas, Brazil
        }{
        Thomas Adam Academic Center -- Poços de Caldas, Brazil
        }}
    \textit{President \hfill Nov 2021 - Oct 2022}
        \begin{itemize}
            \item Advocated for students' rights, successfully implementing a half-fare program and an exclusive transportation line.
            \item Coordinated the Federal Institute of E-Sports Tournament (TEIF) to promote community integration and teamwork.
            \item Acted as the primary mediator in conflict resolution between students and the institution's leadership.
        \end{itemize}

\section{Skills}
    % Keep this section concise and relevant to your target jobs
    \begin{itemize}
        \item \textbf{Technical:} PHP, Laravel, JavaScript, TypeScript, NodeJS, VueJS, MySQL, Git, Scrum, Agile
        \item \textbf{Language:} Portuguese (Native), English (B1), Spanish (A1)
    \end{itemize}

\end{document}
